### 2020-09-16 paper/appendA.tex
Fixes

\begin{defnTwo}[Artemis graph]
  A graph $G$ is an \emph{Artemis graph} if it contains no odd hole, no antihole of length at least five, and no prism.
\end{defnTwo}

@@

\begin{defnTwo}[local subset of a prism]
  A subset $X \subseteq V(K)$ is \emph{local} if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
  \label{def:localSubOfPrism}
\end{defnTwo}

@@

\begin{defnTwo}[major neighbor of a hyperprism]
  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if it is a major neighbor of some instance of $H$.
\end{defnTwo}

\begin{defnTwo}[local subset of a hyperprism]
  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
\end{defnTwo}

\begin{defnTwo}[maximal hyperprism]
  A hyperprism $H$ is \emph{maximal} if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
\end{defnTwo}

@@

\begin{defnTwo}[appearance of a graph]
  Given a graph $G$, and \emph{appearance} of a graph $J$ is any induced subgraph of $G$ that is isomorphic to the line graph $L(H)$ of a bipartite subdivision $H$ of $J$. An appearance of $J$ is \emph{degenerate} if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
\end{defnTwo}

@@

\begin{defnTwo}[overshadowed appearance]
  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
\end{defnTwo}

@@

\begin{defnTwo}[saturating $J$-strip system]
  $X \subseteq V(G)$ \emph{saturates} the strip system if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. a strip system]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if the set of its neighbors saturates the strip system.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
\end{defnTwo}

\begin{defnTwo}[subset local w.r.t. a strip system]
  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
\end{defnTwo}

@@

\begin{itemize}
	\item $a :\in X$, when $X$ is a set -- let $a$ be equal to any element of $X$,
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors,
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors,
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$,
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$,
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$,
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$,
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$,
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$,
	\item $[n]$  -- $\{1, \ldots, n\}$,
	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.
\end{itemize}

>>>>

\begin{defnTwo}[Artemis graph]
  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd hole, no antihole of length at least five, and no prism.
\end{defnTwo}

@@

\begin{defnTwo}[local subset of a prism]
  A subset $X \subseteq V(K)$ is \emph{local} if and only if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
  \label{def:localSubOfPrism}
\end{defnTwo}

@@

\begin{defnTwo}[major neighbor of a hyperprism]
  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if and only if it is a major neighbor of some instance of $H$.
\end{defnTwo}

\begin{defnTwo}[local subset of a hyperprism]
  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if and only if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
\end{defnTwo}

\begin{defnTwo}[maximal hyperprism]
  A hyperprism $H$ is \emph{maximal} if and only if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
\end{defnTwo}

@@

\begin{defnTwo}[appearance of a graph]
  Given a graph $G$, and \emph{appearance} of a graph $J$ is any induced subgraph of $G$ that is isomorphic to the line graph $L(H)$ of a bipartite subdivision $H$ of $J$. An appearance of $J$ is \emph{degenerate} if and only if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
\end{defnTwo}

@@

\begin{defnTwo}[overshadowed appearance]
  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if and only if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
\end{defnTwo}

@@

\begin{defnTwo}[saturating $J$-strip system]
  $X \subseteq V(G)$ \emph{saturates} the strip system if and only if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. a strip system]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if and only if the set of its neighbors saturates the strip system.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if and only if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
\end{defnTwo}

\begin{defnTwo}[subset local w.r.t. a strip system]
  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if and only if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
\end{defnTwo}

@@

\begin{itemize}
	\item $a :\in X$, when $X$ is a set -- let $a$ be equal to any element of $X$,
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
	\item $a - b$, when $a$ and $b$ are vertices -- $a$ and $b$ are neighbors,
	\item $a \cdots b$, when $a$ and $b$ are vertices -- $a$ and $b$ are not neighbors,
	\item $a - X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a neighbor in $X$,
	\item $a \cdots X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a nonneighbor in $X$,
	\item $a \blacktriangleleft  X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is complete to $X$,
	\item $a \ntriangleleft X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is anticomplete to $X$,
	\item $X \setComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is complete to $Y$,
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is anticomplete to $Y$,
	\item $[n]$  -- $\{1, \ldots, n\}$,
	\item \LGBSK -- the line-graph of a bipartite subdivision of $K_4$.
\end{itemize}

### 2020-09-16 paper/coloringBergeGraphs.tex
Fixes

A natural problem for perfect graphs is a problem of coloring them. In 1988 Gr\"otschel et al. published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}. We consider it in \Cref{sec:coloringEllipsoid}. However due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.

There has been much progress on the quest of finding a more classical algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this. \todo{better wording of this paragraph}

@@

For a channel defined by a graph $C_5$, using five messages of length 2 to communicate gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\alpha(C_5^2)$).

Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.  Open it up to the point where non-consecutive ribs are orthogonal, i.e., form an angle of 90$^\circ$. This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors. See \Cref{fig:umbrella}. We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.

@@

It turns out, that we can obtain a similar representation of the nodes of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^{3k}$, so that any two non-adjacent nodes are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}). Moreover, we still get $e_1^\intercal v_i = 5^{-k/4}$ for every $i \in V(C_5^k)$ (the proof is quite technical and we omit it here).

@@

It turns out that this method extends to any graph $G$ in place of $C_5$. All we have to do is to find a orthogonal representation that will give us the best bound. So, we can define the \emph{Lovász number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
$$\vartheta(G) = \min\limits_{c,U} \max\limits_{i\in V} \frac{1}{(c^\intercal u_i)^2},$$

@@

We may think equivalently of $n \times n$ matrices as vectors with $n^2$ coordinates.
\begin{defn}[convex cone]
  A subset $C$ of $\mathbb{R}^n$ is a \emph{convex cone}, if for any positive scalars $\alpha, \beta$ and for any $x, y \in C$, $\alpha x + \beta y \in C$.
\end{defn}

@@

Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all nonedges $ij$. An \emph{orthonormal} representation is an orthogonal representation with $|u_i| = 1$ for all $i$. The \emph{angle} of an orthogonal representation is the smallest half-angle of a rotational cone containing the representing vectors.

@@

\begin{algorithmic}[1]
  \mProcedure{Get-Max-Stable-Set}{$G$}
  \ls $v_1, \ldots, v_n \gets$ an ordering of $V(G)$
  \ls $G_0 \leftarrow G$
  \ls $\alpha_G = \alpha(G)$
  \mForEach{$1 \leq i \leq |V|$}
    \mIf{$\alpha(G_{i-1} \setminus v_i) = \alpha_G$}
      \ls $G_i \leftarrow G_{i-1} \setminus \{v_i\}$
    \mElse
      \ls $G_i \leftarrow G_{i-1}$
    \mEndIf
  \mEndFor
  \ls \RETURN $G_{|V|}$
  \mEndProcedure
\end{algorithmic}

@@

  The running time of \Cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
\end{proof}

@@

We create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the nodes $v$, $u$ are adjacent in $G$. Then we can calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.

@@

In 2005 Maffray and Trotignon a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}. They later improved the time complexity to $O(|V|^2|E|)$ \cite{coloringArtemis}.

@@

The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement. The main idea is that, if square-free Berge graph $G$ is a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism. We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively. The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward. We provide its pseudocode in the Appendix A.

>>>>

A natural problem for perfect graphs is a problem of coloring them. In 1988 Gr\"otschel et al. published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}. We consider it in \Cref{sec:coloringEllipsoid}. However due to its use of the ellipsoid method, this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.

There has been much progress on the quest of finding an algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.

@@

For a channel defined by a graph $C_5$, using five messages of length 2 to communicate gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\sqrt{\alpha(C_5^2)}$).

Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.  Open it up to the point where non-consecutive ribs are orthogonal, i.e., form an angle of 90$^\circ$. This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots, u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent vertices are represented with orthogonal vectors. See \Cref{fig:umbrella}. We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.

@@

It turns out, that we can obtain a similar representation of the vertices of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^{3k}$, so that any two non-adjacent vertices are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}). Moreover, we still get $e_1^\intercal v_i = 5^{-k/4}$ for every $i \in V(C_5^k)$ (the proof is quite technical and we omit it here).

@@

It turns out that this method extends to any graph $G$ in place of $C_5$. All we have to do is to find a orthogonal representation that will give us the best bound. So, we can define the \emph{Lovász number} of a graph $G$ as:
$$\vartheta(G) = \min\limits_{c,U} \max\limits_{i\in V} \frac{1}{(c^\intercal u_i)^2},$$

@@

We may think equivalently of $n \times n$ matrices as vectors with $n^2$ coordinates.
\begin{defn}[convex cone]
  A subset $C$ of $\mathbb{R}^n$ is a \emph{convex cone}, if and only if for any positive scalars $\alpha, \beta$ and for any $x, y \in C$, $\alpha x + \beta y \in C$.
\end{defn}

@@

Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all anticonnected vertices $i, j$. An \emph{orthonormal} representation is an orthogonal representation with $|u_i| = 1$ for all $i$. The \emph{angle} of an orthogonal representation is the smallest half-angle of a rotational cone containing the representing vectors.

@@

\begin{algorithmic}[1]
  \mProcedure{Get-Max-Stable-Set}{$G$}
  \ls $v_1, \ldots, v_n \gets$ vertices of $G$
  \ls $G_0 \leftarrow G$
  \ls $\alpha_G = \alpha(G)$
  \mForEach{$1 \leq i \leq |V|$}
    \mIf{$\alpha(G_{i-1} \setminus v_i) = \alpha_G$}
      \ls $G_i \leftarrow G_{i-1} \setminus \{v_i\}$
    \mElse
      \ls $G_i \leftarrow G_{i-1}$
    \mEndIf
  \mEndFor
  \ls \RETURN $G_{|V|}$
  \mEndProcedure
\end{algorithmic}

@@

  The running time of \Cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once with additional $O(|V|^2)$ time for constructing the graph.
\end{proof}

@@

We create graph $G'$ by replacing every vertex $v$ by a set $W_v$ of $w(v)$ nonadjacent vertices, making two vertices $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the vertices $v$, $u$ are adjacent in $G$. Then we can calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.

@@

In 2005 Maffray and Trotignon showed a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}. They later improved the time complexity to $O(|V|^2|E|)$ \cite{coloringArtemis}.

@@

The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement. The main idea is that, if square-free Berge graph $G$ is not a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism. We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively. The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward. We provide its pseudocode in the Appendix A.

### 2020-09-16 paper/definitions.tex
Fixes

An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ denote the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is, all vertices $y$ such that $xy$ is an edge. Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

@@

\begin{defn}[subgraph]
  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subseteq V$ and $E' \subseteq E$.
\end{defn}

@@

\begin{defn}[$X$-completeness]
  Given set $X \subseteq V$, vertex $v \notin X$ is \emph{$X$-complete} if it is adjacent to every node $x \in X$. A set $Y \subseteq V$ is $X$-complete if $X \cap Y = \emptyset$ and every node $y \in Y$ is $X$-complete.
\end{defn}

@@

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$. Notice that we don't allow any edges other than the ones between consecutive vertices for a graph to be called a path.

@@

\begin{defn}[connected graph, subset]
  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$.
  A subset $X \subseteq V(G)$ is connected if the graph $G[X]$ is connected.
\end{defn}

@@

Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.

@@

If a path, a cycle or a hole has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.

\begin{defn}[complement]
  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is, two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
\end{defn}

@@

\begin{defn}[anticonnected graph, subset]
  A graph $G$ is \emph{anticonnected} if $\overline{G}$ is connected.
  A subset $X$ is \emph{anticonnected} if $\overline{G}[X]$ is connected.
\end{defn}

@@

\begin{defn}[anticlique]
  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets} or \emph{stable sets}. 
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.

@@

\begin{defn}[coloring]
  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that $c(x) \neq c(y)$ for every edge $xy \in E(G)$. A $k$-coloring of $G$ (if exists) is a coloring, such that $c(x) \leq k$ for all vertices $x \in V(G)$.
\end{defn}

>>>>

An edge $\{x, y\}$ is said to \emph{join}, or \emph{be between} vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ denote the same edge (all our graphs are \emph{undirected}). If $xy \in E(G)$ then $x$ and $y$ are \emph{adjacent}, \emph{connected} or \emph{neighboring}. By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is, all vertices $y$ such that $xy$ is an edge. Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the \emph{neighborhood} of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

@@

\begin{defn}[subgraph]
  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if and only if $V' \subseteq V$ and $E' \subseteq E$.
\end{defn}

@@

\begin{defn}[$X$-completeness]
  Given a graph $G = (V, E)$ and a set $X \subseteq V$, vertex $v \in V(G) \setminus X$ is \emph{$X$-complete} if and only if it is adjacent to every vertex $x \in X$. A set $Y \subseteq V$ is $X$-complete if and only if $X \cap Y = \emptyset$ and every vertex $y \in Y$ is $X$-complete.
\end{defn}

@@

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1$-$x_2$-$\ldots$-$x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$. Notice that we don't allow any edges other than the ones between consecutive vertices for a graph to be called a path.

@@

\begin{defn}[connected graph, subset]
  A graph $G$ is \emph{connected} if and only if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$.
  A subset $X \subseteq V(G)$ is connected if and only if the graph $G[X]$ is connected.
\end{defn}

@@

@@

If a path, a cycle or a hole has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}. Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
\begin{defn}[complement]
  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is, two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
\end{defn}

@@

\begin{defn}[anticonnected graph, subset]
  A graph $G$ is \emph{anticonnected} if and only if $\overline{G}$ is connected.
  A subset $X$ is \emph{anticonnected} if and only if $\overline{G}[X]$ is connected.
\end{defn}

@@

\begin{defn}[anticlique]
  An \emph{independent set} or an \emph{anticlique} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.

@@

\begin{defn}[coloring]
  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that for every edge $xy \in E(G)$, $c(x) \neq c(y)$ . A $k$-coloring of $G$ (if exists) is a coloring, such that $c(x) \leq k$ for all vertices $x \in V(G)$.
\end{defn}
